\huge A Usability Evaluation of Tor Launcher

### 2017-03-22 pets2017-paper/pets2017-paper.tex
Remove duplicate paragraph
It appeared as a merge conflict after the order got swapped in
39bbc3a04db961e435e01a95550d8db268900d0b
handle rest of shepherd todos

\section{Introduction}
Tor~\cite{dingledine2004tor} is an anonymity network that routes Internet traffic through a series of relays 
to make it difficult to observe sources and destinations.
Tor Browser~\cite{torbrowser} is a modified Firefox browser that routes traffic through Tor, designed to minimize the configuration required before connecting.
Although Tor was originally designed for anonymity, many now use it to circumvent Internet censorship.
Because of this, many countries block Tor relays specifically to prevent their citizens from circumventing censorship~\cite{winter2012great}.

@@

\section{Methodology} 
This section discusses our usability testing process, including the simulated censorship environments we used to require users to configure different network components to connect to Tor and the evaluation metrics  we collected.

@@

We kept the user involved in the configuration so that they explicitly start a connection to Tor (currently, the user needs to click a ``connect'' button before Tor Launcher makes a connection to Tor). 
%We chose not to leverage user inputs such as their location, risk, or other preferences, as this would require additional research on all these options before designing changes incorporating those. 
And although some users in our qualitative study tried to configure unnecessary components, we still also allow all users to choose a manual configuration to give them a chance to connect to Tor securely the first time. 
We limited our design changes to ones that do not require infrastructural changes or cause additional financial burden to make it easier for the Tor project to adopt them.

@@

Figure~\ref{fig:time_to_success_ecdf} shows the cumulative distribution of connection times. Everyone in E1 was able to connect right away; participants with the NEW interface were faster than participants with the OLD interface. Most participants in E2 were able to connect right away, with participants with the NEW interface and OLD interface taking a similar amount of time. Participants in E3 took various amount of time to succeed, with participants with the NEW interface connecting significantly faster than those with the OLD interface.

@@

>>>>

\section{Introduction}
Tor~\cite{dingledine2004tor} is an anonymity network that routes Internet traffic through a series of relays 
to make it difficult to observe sources and destinations.
Tor Browser~\cite{torbrowser} is a modified Firefox browser that routes traffic through the Tor network.
Although Tor and Tor Browser were originally designed for anonymity, many now use them to circumvent Internet censorship.
Because of this, many countries block Tor relays specifically to prevent their citizens from circumventing censorship~\cite{winter2012great}.

@@

\section{Methodology} 
This section discusses our IRB-approved usability testing process, including the simulated censorship environments we used to require users to configure different network components to connect to Tor and the evaluation metrics  we collected.

@@

We kept the user involved in the configuration so that they explicitly start a connection to Tor (currently, the user needs to click a ``connect'' button before Tor Launcher makes a connection to Tor). 
%We chose not to leverage user inputs such as their location, risk, or other preferences, as this would require additional research on all these options before designing changes incorporating those. 
And although some users in our qualitative study tried to configure unnecessary components in confusion, we still give users the freedom to configure optional components. 
We limited our design changes to ones that do not require infrastructural changes or cause additional financial burden to make it easier for the Tor project to adopt them.

@@

Figure~\ref{fig:time_to_success_ecdf} shows the cumulative distribution of connection times. Everyone in E1 was able to connect right away; participants with the NEW interface were faster than participants with the OLD interface. Most participants in E2 were able to connect right away, with participants with the NEW interface and OLD interface taking a similar amount of time. Participants in E3 took various amounts of time to succeed, with participants with the NEW interface connecting significantly faster than those with the OLD interface.

@@

Although none of the participants needed to configure a proxy to bypass censorship, participants still spent time trying to configure them. Participants the OLD interface spent more time configuring proxies than bridges and participants with the NEW interface spent about an equal amount of time configuring bridges and proxies even when the interface said that they didn't need one.
